Preparing data from the Global Burden of Disease for METAHIT modelling

### 2021-10-18 data-raw/gbd_process.Rmd
Remission rates can be a smooth function of age

```{r}
library(tidyverse)
library(progress)
library(tempdisagg)
relative_path_gbd <- "~/scratch/chronic/metahit_data"

@@

saveRDS(gbddb, file=file.path(relative_path_gbd, "gbddb.rds"))
saveRDS(gbddb, file=file.path("~/work/chronic/disbayes/metahit", "gbddb.rds"))

qbeta(c(0.025, 0.975), 128, 940-128) # 0.11 to 0.16.more plausible

>>>>

```{r}
library(tidyverse)
library(progress)
library(tempdisagg)
relative_path_gbd <- "~/scratch/chronic/metahit_data/2017"

@@
